\thispagestyle{plain}
\begin{center}
	
	\LARGE
	\textbf{Acknowledgements}
	
\end{center}
\vspace{100pt}

This research could not have been performed without the assistance, patience, and support of many individuals.\\

On behalf of the historical expertise required for this research, I would like to thank the Geschichtsarchiv Langwasser, including Mrs. Edith Schroth and Mr. Alfred Schroth for their constant support in providing old photographs, material and making contact to various institutions like archives, museums and companies. They initiated the contact with the Altstadtfreunde Nürnberg e.V. as well.\\
Additionally I would like to thank the Altstadtfreunde Nürnberg e.V. for a significant amount of historic pictures and professional guidance regarding the history of the Pellerhaus. I am thankful for the opportunity to be supported by chairman Mr. Karl-Heinz Enderle during my research.\\

Secondly, I must thank my thesis advisor, Mr. Prof. Dr. Stefan Röttger for mentoring me during my undergraduate studies. He proved his confidence in me by encouraging me to teach computer graphics to other students, letting me demonstrate how much fun it can be to create graphics with the open source 3D graphics suite Blender, and offered me several jobs in 3D animation. His insight lead to the initial proposal to examine the possibility of reconstructing the Pellerhaus facade. In addition I would like to extend my gratitude to Mr. Prof. Dr. (USA) Ralph Lano for supervision during my studies. His teaching style and enthusiasm made a strong impression on me and I have always carried positive memories of the classes I attended. Although the classes I took were not mandatory and rather rare they made a lot of fun (e.g. XBox programming with Unity), he was always very helpful and friendly. I would like to thank you very much for your support and understanding over these past four years.\\

Finally I would like to extend my deepest gratitude to my family without whose love, support and understanding I could never have completed this bachelor's degree.
